An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-15 paper/paper.tex
Paper: more proofreading

\begin{table}
\begin{center}
    \begin{tabular}{| l | l |} 
    \hline
    Node IP & Self explanatory \\ \hline
    Blacklisters & List of peers who consider this node unreliable\\ \hline
    Backed Up Files & List of information on files this peer has backed up \\ \hline
    Stored Files & List of information on files this node stores for other peers \\ \hline
    \end{tabular}
    \caption{Summary of a metadata record}
    \label{tab:metadataRecord}
\end{center}
\end{table}

>>>>

\begin{table}
\begin{center}
    \begin{tabular}{| l | l |} 
    \hline
    Node IP & The most recent IP address used by this node\\ \hline
    Blacklisters & List of peers who consider this node unreliable\\ \hline
    Backed Up Files & List of information on files this peer has backed up \\ \hline
    Stored Files & List of information on files this node stores for other peers \\ \hline
    \end{tabular}
    \caption{Summary of a metadata record}
    \label{tab:metadataRecord}
\end{center}
\end{table}
